---
title: "JMS 2022"
author: "Chishu Yin"
date: "2022/5/16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
a <- function(pr,pt,fi)
{
  1+(fi-1)*(pr+pt)
}

b <- function(pr,pt,fi)
{
  -4*fi*(fi-1)*pr*pt
}

##p11,p12,p21,p22
prob <- function(pr,pt,fi)
{
  if(fi==1)
  {
    p<-c(pr*pt,pr-pr*pt,pt-pr*pt,1-pr-pt+pr*pt)
    p
  }
  else{
  a<- 1+(fi-1)*(pr+pt)
  b <- -4*fi*(fi-1)*pr*pt
  p <- matrix(nrow = 2, ncol = 2)
  p[1,1] <- round(( a - ( a^2+b )^(0.5) ) / (2*(fi-1)),digits = 4)
  p[1,2] <- round(pr-p[1,1],digits = 4)
  p[2,1] <- round(pt-p[1,1],digits = 4)
  p[2,2] <- round(1 - p[1,1] - p[1,2] - p[2,1],digits = 4)
  p <- c(p[1,1],p[1,2],p[2,1],p[2,2])
  p}
}
```





```{r}
p_e0<-0.7
p_s0<-0.6
delta_e2 <- 0.1
delta_s2 <- 0.1

ee<-seq(0,1,length.out=30)
ss<-seq(0,1,length.out=30)

result<- matrix(data = NA, nrow = 30, ncol = 30)

for(mm in 1:30)
{
  for(kk in 1:30)
  {
    p_e<- c(p_e0,p_e0, ee[kk])
    p_s<- c(p_s0,p_s0, ss[mm])
    
    k<- length(p_e) -1
    phi <- 2

    p <- matrix(data=NA,nrow = k+1,ncol=4)

    for(i in 1: (k+1))
    { 
      p[i,] <- prob(p_e[i],p_s[i],phi)
    }
    
n1<-10
n2<-10
r1<-1
r2<-2
t1<-1
t2<-2
N<-10000
x0<-rmultinom(N,n1,p[1,])
x<-matrix(data = NA,nrow = k, ncol = N)

x1<-rmultinom(N,n1,p[2,])
x2<-rmultinom(N,n1,p[3,])

s<-0
for(i in 1:N)
{
  
  if( (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))>=t1)
  {
    if((x1[1,i]+x1[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i]))>=t1 & (x2[1,i]+x2[2,i]-(x1[1,i]+x1[2,i]))> 0)
    {
      s<-s+1
    }
    else if((x1[1,i]+x1[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i]))>=t1 & (x2[1,i]+x2[2,i]-(x1[1,i]+x1[2,i]))==0)
    {
      s<-s+1/k
    }
    else if((x1[1,i]+x1[2,i]-(x0[1,i]+x0[2,i]))<r1 | (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i]))<t1)
    {
      s<-s+1
    }
  }

}
result[mm,kk]<-s/N
    
    
  }
}



```

```{r}
#for(i in 1:30)
#{
#  plot(ee,result[i,],main = ss[i],ylim = c(0.25,0.4))
#}

which.min(result)
result[900]
result[1]
PCS<-result
p_s2<-ss
p_e2<-ee
persp(p_s2,p_e2,PCS)


```






Want the function $P(X_{11}+X_{12}-(Y_{11}+Y_{12})=r_1,X_{11}+X_{21}-(Y_{11}+Y_{21})=t_1)$

```{r}
multibin_prob<-function(r1,t1,n1,p1,p2)
{

  summ<-0
  for (i in 0:(n1-r1)) {
    for(j in 0:max(r1+i,0)){
      for(k in 0:i){
        for(l in 0:min(n1-i,n1+j-k-t1-i-r1)){
          if(l<0 | (r1+i-j)<0 | (t1+k-j+l)<0 | (n1-j-(r1+i-j)-(t1+k-j+l))<0 | (n1-k-(i-k)-(l))<0){next}
          else{
          x <- c( (j) , (r1+i-j) , (t1+k-j+l) , (n1-j-(r1+i-j)-(t1+k-j+l) ))
          #print(x)
          #print(c(i,j,k,l,00000))
          y <- c( k , i-k, l , (n1-k-(i-k)-(l)) )
          #print(y)
          summ <- summ + dmultinom(x, size = NULL, prob = p1, log = FALSE)*dmultinom(y, size = NULL, prob = p2, log = FALSE)
        
        }}
      }
    }
    
  }
 summ
}

multibin_prob(3,-1,17,c(0.2815, 0.6185, 0.0185, 0.0815), c(0.2384, 0.4616, 0.0616, 0.2384))

```






Want the function $P(X_{11}+X_{12}-(Y_{11}+Y_{12})=r_1,X_{11}+X_{21}-(Y_{11}+Y_{21})=t_1)$

```{r}
#p1 treatment; p2 control
multibin_prob<-function(r1,t1,n1,p1,p2)
{

  summ<-0
  for (i in 0:(n1-r1)) {
    for(j in 0:max(r1+i,0)){
      for(k in 0:i){
        for(l in 0:min(n1-i,n1+j-k-t1-i-r1)){
          if(l<0 | (r1+i-j)<0 | (t1+k-j+l)<0 | (n1-j-(r1+i-j)-(t1+k-j+l))<0 | (n1-k-(i-k)-(l))<0){next}
          else{
          x <- c( (j) , (r1+i-j) , (t1+k-j+l) , (n1-j-(r1+i-j)-(t1+k-j+l) ))
          #print(x)
          #print(c(i,j,k,l,00000))
          y <- c( k , i-k, l , (n1-k-(i-k)-(l)) )
          #print(y)
          summ <- summ + dmultinom(x, size = NULL, prob = p1, log = FALSE)*dmultinom(y, size = NULL, prob = p2, log = FALSE)
        
        }}
      }
    }
    
  }
 summ
}

multibin_prob(3,-1,17,c(0.2815, 0.6185, 0.0185, 0.0815), c(0.2384, 0.4616, 0.0616, 0.2384))

```


$P(X_{e1}-Y_{e1}\geq e_1, X_{s1}-Y_{s1} \geq s_1, X_{e1}+X_{e2} - (Y_{e1}+Y_{e2}) \geq e_2, X_{s1}+X_{s2}- (Y_{s1}+Y_{s2}) \geq s_2)$
```{r}
#p1 treatment, p2 is control
cumu_fct1 <- function(e1,e2,s1,s2,n1,n2,p1,p2)
{
  s<-0
  for(i in e1:n1)
  {
    for(j in s1 : n1)
    {
      for(k in max(0,e2-i):n2)
      {
        for(l in max(0,s2-j):n2)
        {
          s<-s+ multibin_prob(i,j,n1,p1,p2)*multibin_prob(k,l,n2,p1,p2)
        }
      }
    }
  }
  s
}
```






$P(X_{s1} - Y_{s1} < s_1)$
```{r}
# p1 treatment, p2 control
cumu_fct2 <- function(s1,n1,p1,p2)
{
  s<-0
  for(i in 0:n1)
  {
    for(j in 0:(s1-1) )
    {
      s<-s+ multibin_prob(i,j,n1,p1,p2)
    }
  }
  s
}
```







$P(Xr=xr,Xt=xt)$
```{r}
#P(Xr=xr,Xt=xt)
joint_prob <- function(xr,xt,n1,p)
{
  sum <- 0
  for(i in max(0,xr+xt-n1) : min(xr,xt))
  {
    if(i<0 | xr-i<0 | xt-i<0 | n1-xr-xt+i<0)
    {
      sum<-sum+0
    }
    else{
    x <- c( i , xr-i , xt-i , n1-xr-xt+i )
    sum <- sum + dmultinom(x, size = NULL, prob = p, log = FALSE)
    ##cat("s = ", sum,"x =", x, "\n")
    }
  }
  sum
}
```








function for k=2, PCS1-1 delta1=delta2, note shizi page 2-3
```{r}
#p0 control; p1, p2 are treatments, p2 selected
fct_PCS11 <- function(e1,e2,s1,s2,n1,n2,p0,p1,p2)
{
  s<-0
  for( i in 0: min(n1-e1,n1) )
  {
    for( j in max(1-s1,0): min(n1,n1-s1))
    {
      for( k in 0 : n1)
      {
        for( l in 0 : max(min(n1,s1+j-1),0) )
        {
          for( a in max(min(e1+i,n1),0) : n1)
          {
            for( b in max(min(s1+j,n1),0) : n1)
            {
              for( c in 0 : min(n2+a-i-e2,n2) )
              {
                for( d in 0 : min(n2+b-j-s2,n2))
                {
                  for(e in max(min(e2+i+c-a,n2),0) : n2)
                  {
                    for(f in max(min(s2+j+d-b,n2),0) : n2)
                    {
                      
                     #if(   s1+j-1<0 | e1+i>n1  | s1+j>n1 | e2+i+c-a>n1  | s2+j+d-b>n1 )
                      #if( n2+a-i-e2<0 | n2+b-j-s2<0 | i<0 | j<0 | k<0 | l<0 | a<0 | b<0| c<0| d<0 | e<0 | f<0)
                      #{
                      #  s<-s+0
                      #}
                      
                      #else
                      {
                        s <- s + joint_prob(i,j,n1,p0) * joint_prob(k,l,n1,p1) * joint_prob(a,b,n1,p2) * joint_prob(c,d,n2,p0) * joint_prob(e,f,n2,p2)
                      }
                      
                      
                      
                      
                    }
                  }
                }
              }
            }
          }
        }
      }
    }
  }
  s
}
```

test
```{r}
n1<-4
n2<-10
r1<-1
r2<-2
t1<-0
t2<-5
p0<-p[1,] #control
p1<-p[2,]
p2<-p[3,]

fct_PCS11(r1,r2,t1,t2,n1,n2,p0,p1,p2)
```


#simulation PCS11
```{r}
s<-0
N<-100000

x0<-rmultinom(N,n1,p[1,])
# x<-matrix(data = NA,nrow = k, ncol = N)
x1<-rmultinom(N,n1,p[2,])
x2<-rmultinom(N,n1,p[3,])

xx0<-rmultinom(N,n2,p[1,])
#x<-matrix(data = NA,nrow = k, ncol = N)
xx1<-rmultinom(N,n2,p[2,])
xx2<-rmultinom(N,n2,p[3,])


for( i in 1:N)
{
  if( (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))>=t1  &  (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))  +  (xx2[1,i]+xx2[2,i]-(xx0[1,i]+xx0[2,i]))   >=r2 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))   +  (xx2[1,i]+xx2[3,i]-(xx0[1,i]+xx0[3,i]))  >=t2)
  {
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) < t1 )
    {
      s<-s+1
    }
  }

}
s/N
```


function for k=2, PCS1-2 delta1=delta2, note shizi page 2-3
```{r}
#p0 control; p1, p2 are treatments, p2 selected
fct_PCS12 <- function(e1,e2,s1,s2,n1,n2,p0,p1,p2)
{
  s<-0
  for(i in 0: min(n1,n1-e1))
  {
    for(j in 0 : min(n1,n1-s1))
    {
      for(k in 0 : (n1-1))
      {
        for(l in max(s1+j,0) : n1)
        {
          for(a in max(max(e1+i,k+1),i+e2-n2) : n1)
          {
            for(b in max(max(s1+j,0),s2+j-n2) : n1)
            {
              for(c in 0: min(n2, n2+a-i-e2))
              {
                for(d in 0 : min(n2, n2+b-s2-j))
                {
                  for(e in max(e2+i+c-a,0) : n2)
                  {
                    for(f in max(s2+j+d-b,0) : n2)
                    {
                       s <- s + joint_prob(i,j,n1,p0) * joint_prob(k,l,n1,p1) * joint_prob(a,b,n1,p2) * joint_prob(c,d,n2,p0) * joint_prob(e,f,n2,p2)
                    }
                  }
                }
              }
            }
          }
        }
      }
    }
  }
  s
}
```  


test
```{r}
n1<-4
n2<-10
r1<-1
r2<-2
t1<-0
t2<-5
p0<-p[1,] #control
p1<-p[2,]
p2<-p[3,]

fct_PCS12(r1,r2,t1,t2,n1,n2,p0,p1,p2)
```


#simulation PCS12
```{r}
s<-0
N<-1000000

x0<-rmultinom(N,n1,p[1,])
# x<-matrix(data = NA,nrow = k, ncol = N)
x1<-rmultinom(N,n1,p[2,])
x2<-rmultinom(N,n1,p[3,])

xx0<-rmultinom(N,n2,p[1,])
#x<-matrix(data = NA,nrow = k, ncol = N)
xx1<-rmultinom(N,n2,p[2,])
xx2<-rmultinom(N,n2,p[3,])


for( i in 1:N)
{
  if( (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))>=t1  &  (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))  +  (xx2[1,i]+xx2[2,i]-(xx0[1,i]+xx0[2,i]))   >=r2 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))   +  (xx2[1,i]+xx2[3,i]-(xx0[1,i]+xx0[3,i]))  >=t2)
  {
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]> x1[1,i]+x1[2,i])
    {
      s<-s+1
    }
  }

}
s/N
```









function for k=2, PCS1-3 delta1=delta2, note shizi page 2-3
```{r}
#p0 control; p1, p2 are treatments, p2 selected
fct_PCS13 <- function(e1,e2,s1,s2,n1,n2,p0,p1,p2)
{
  s<-0
  for(i in 0: min(n1,n1-e1))
  {
    for(j in 0 : min(n1,n1-s1))
    {
      for(k in max(e1+i,0) : n1)
      {
        for(l in max(s1+j,0) : n1)
        {
          
          {
            for(b in max(max(s1+j,0),s2+j-n2) : n1)
            {
              for(c in 0: min(n2, n2+k-i-e2))
              {
                for(d in 0 : min(n2, n2+b-s2-j))
                {
                  for(e in max(e2+i+c-k,0) : n2)
                  {
                    for(f in max(s2+j+d-b,0) : n2)
                    {
                       s <- s + joint_prob(i,j,n1,p0) * joint_prob(k,l,n1,p1) * joint_prob(k,b,n1,p2) * joint_prob(c,d,n2,p0) * joint_prob(e,f,n2,p2)
                    }
                  }
                }
              }
            }
          }
        }
      }
    }
  }
  s/2
}
```  


test
```{r}
n1<-4
n2<-10
r1<-1
r2<-2
t1<-0
t2<-5
p0<-p[1,] #control
p1<-p[2,]
p2<-p[3,]

fct_PCS13(r1,r2,t1,t2,n1,n2,p0,p1,p2)
```


#simulation PCS13
```{r}
s<-0
N<-1000

x0<-rmultinom(N,n1,p[1,])
# x<-matrix(data = NA,nrow = k, ncol = N)
x1<-rmultinom(N,n1,p[2,])
x2<-rmultinom(N,n1,p[3,])

xx0<-rmultinom(N,n2,p[1,])
#x<-matrix(data = NA,nrow = k, ncol = N)
xx1<-rmultinom(N,n2,p[2,])
xx2<-rmultinom(N,n2,p[3,])


for( i in 1:N)
{
  if( (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))>=t1  &  (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))  +  (xx2[1,i]+xx2[2,i]-(xx0[1,i]+xx0[2,i]))   >=r2 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))   +  (xx2[1,i]+xx2[3,i]-(xx0[1,i]+xx0[3,i]))  >=t2)
  {
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]== x1[1,i]+x1[2,i])
    {
      s<-s+1/2
    }
  }

}
s/N
```







#PCS1=PCS11+PCS12+PCS13
```{r}
#p0 control; p1, p2 are treatments, p2 selected
fct_PCS1 <- function(e1,e2,s1,s2,n1,n2,p0,p1,p2)
{
  fct_PCS11(e1,e2,s1,s2,n1,n2,p0,p1,p2)+fct_PCS12(e1,e2,s1,s2,n1,n2,p0,p1,p2)+fct_PCS13(e1,e2,s1,s2,n1,n2,p0,p1,p2)
}
```









#Find LFC
```{r}
p_e0<-0.7
p_s0<-0.5
delta_e1<-0.05
delta_s1<-0.05
delta_e2 <- 0.15
delta_s2 <- 0.15

ee<-seq(0,1,length.out=10)
ss<-seq(0,1,length.out=10)

result<- matrix(data = NA, nrow = 10, ncol = 10)

for(mm in 1:10)
{
  for(kk in 1:10)
  {
    p_e<- c(p_e0,ee[kk],ee[kk])
    p_s<- c(p_s0,ss[mm], ss[mm])
    
    k<- length(p_e) -1
    phi <- 2

    p <- matrix(data=NA,nrow = k+1,ncol=4)

    for(i in 1: (k+1))
    { 
      p[i,] <- prob(p_e[i],p_s[i],phi)
    }
    
n1<-4
n2<-10
r1<-1
r2<-2
t1<-1
t2<-2

result[mm,kk]<- fct_PCS1(r1,r2,t1,t2,n1,n2,p[1,],p[2,],p[3,])
    
    
  }
}



```


```{r}
result100<-result
```



```{r}
#for(i in 1:30)
#{
#  plot(ee,result[i,],main = ss[i],ylim = c(0.25,0.4))
#}

which.min(result)
result[400]
PCS<-result
pe_1<-ee
ps_1<-ss
persp(ps_1,pe_1,PCS)

#result100<-result

```



Derivative
phi=2
```{r}
fun_multinomial <- expression( factorial(n)/(factorial(i)*factorial(j)*factorial(k)*factorial(n-i-j-k) ) * ( (1+pe+ps - sqrt((1+pe+ps)^2 - 8*pe*ps)/2)  )^i * (pe- (1+pe+ps - sqrt((1+pe+ps)^2 - 8*pe*ps)/2)   )^j * (ps-p11)^k * (1-pe-ps+ (1+pe+ps - sqrt((1+pe+ps)^2 - 8*pe*ps)/2)  )^(n-i-j-k) )

i=1
j=1
k=2
n=5
ps<-0.5
pe<-0.6


#eval(D(fun_multinomial,"p11"))

Deriv_multinomial<-function(i,j,k,n)
{
  (D(fun_multinomial,"p11"))
}


#Deriv_multinomial(1,1,2,5)





g<-deriv(y~factorial(n)/(factorial(i)*factorial(j)*factorial(k)*factorial(n-i-j-k) ) * p11^i * (pe-p11)^j * (ps-p11)^k * (1-pe-ps+p11)^(n-i-j-k),"p11",func = TRUE)
```




Derivative
```{r}
ie2<-1
n1<-9
pe0<-0.5
pek<-pe0+0.1
d<-0
for(k in 0:(n1-ie2)){
s<-0
n2<-10
#print(s)
for (c in (k+1):n2) {
  s<-s+dbinom(c,n2,pe0)*dbinom(c-k-1,n2-1,pek)
}
print(s)
d<- d + s*(dbinom(ie2+k-1,n1-1,pek)-dbinom(ie2+k,n1-1,pek))
}
d
```






Derivative for p_e^k when p_e^k=p_e^1, p_s^k=p_s^1 $\frac{\partial}{\partial p_e^k}P(X_e^k - X_e^0 = e, X_s^k - X_s^0 = s)$ $\phi=1, -n \leq e,s \leq n$ 
```{r}
p_e_deri <-function(e,s,n,pek,pe0,psk,ps0)
{
  sum<-0
  for(i in max(e,0) : min(n,n+e))
  {
    for (j in max(s,0) : min(n,n+s) ) 
    {
      if(i==0)
      {
        sum<-sum + (-n*dbinom(0,n-1,pek)*dbinom(j,n,psk)*dbinom(i-e,n,pe0)*dbinom(j-s,n,ps0))
      }
      else if(i==n)
      {
        sum <- sum + n*dbinom(n-1,n-1,pek)*dbinom(j,n,psk)*dbinom(i-e,n,pe0)*dbinom(j-s,n,ps0)
      }
      else
      {
        sum <- sum + n*(dbinom(i-1,n-1,pek)-dbinom(i,n-1,pek))*dbinom(j,n,psk)*dbinom(i-e,n,pe0)*dbinom(j-s,n,ps0)
      }
    }
  }
  sum
}
```



$P(X_e^k - X_e^0 = e, X_s^k-X_s^0=s)$ $-n \leq e,s \leq n, \phi=1$
```{r}
diff_prob <- function(e,s,n,pek,pe0,psk,ps0)
{
  sum<-0
  for(i in max(e,0): min(n,n+e))
  {
    for(j in max(s,0) : min(n,n+s))
    {
      sum <- sum + dbinom(i,n,pek)*dbinom(j,n,psk)*dbinom(i-e,n,pe0)*dbinom(j-s,n,ps0)
    }
  }
  sum
}
```


Test 
```{r}
e<--2
s<--6
pek<-0.6
pe0<-0.4
psk<-0.7
ps0<-0.4
n<-8

#diff_prob(e,s,n,pek,pe0,psk,ps0)
ss<-0
for( e in (-n):n)
{
  for(s in (-n):n)
  {
    ss<-ss+diff_prob(e,s,n,pek,pe0,psk,ps0)
  }
}
ss




#Simulation
e<--2
s<--6
pek<-0.6
pe0<-0.4
psk<-0.7
ps0<-0.4
n<-8

diff_prob(e,s,n,pek,pe0,psk,ps0)


N<-100000
ss<-0
for(i in 1:N)
{
  xek<-rbinom(1,n,pek)
  xsk<-rbinom(1,n,psk)
  xe0<-rbinom(1,n,pe0)
  xs0<-rbinom(1,n,ps0)
  if(xek-xe0==e & xsk-xs0==s)
  {
    ss<-ss+1
  }
}
ss/N
```


PCS1_1 use diff_prob $P(X_{ke}^1 - X_{0e}^1 \geq e_1, X_{ks}^1 - X_{0s}^1 \geq s_1, X_{ke}^2 -X_{0e}^2 \geq e_2-e_1, X_{ks}^2 - X_{0s}^2 \geq s_2-s_1, X_{is}^1 - X_{0s}^1 < s_1)$ $\phi=1, p_e^k=p_e^1, p_s^k=p_s^1$
```{r}

dif_PCS11 <- function(e1,e2,s1,s2,n1,n2,pek,pe0,psk,ps0)
{
  sum<-0
  for(i in e1 : n1)
  {
    for(j in s1:n1)
    {
      for(k in (e2-i):n2)
      {
        for(l in (s2-j):n2)
        {
          for (a in 0:(s1-1)) 
          {
            for (b in 0:n1) 
            {
              sum<- sum + diff_prob(i,j,n1,pek,pe0,psk,ps0)*diff_prob(k,l,n2,pek,pe0,psk,ps0)*diff_prob(a,b,n1,pek,pe0,psk,ps0)
            }
          }
        }
      }
    }
  }
  sum
}

```


Test
```{r}
e1<-1
e2<-2
s1<-1
s2<-2
n1<-6
n2<-7
pek<-0.7
pe0<-0.5
psk<-0.8
ps0<-0.6
p0<-c(pe0*ps0, pe0- pe0*ps0, ps0- pe0*ps0, 1-pe0-ps0+pe0*ps0)
p2<-c(pek*psk, pek- pek*psk, psk- pek*psk, 1-pek-psk+pek*psk)
p1<-p2

#fct_PCS11(e1,e2,s1,s2,n1,n2,p0,p1,p2)
dif_PCS11(e1,e2,s1,s2,n1,n2,pek,pe0,psk,ps0)
```

#simulation PCS11
```{r}
s<-0
N<-100000

x0<-rmultinom(N,n1,p0)
# x<-matrix(data = NA,nrow = k, ncol = N)
x1<-rmultinom(N,n1,p1)
x2<-rmultinom(N,n1,p2)

xx0<-rmultinom(N,n2,p0)
#x<-matrix(data = NA,nrow = k, ncol = N)
xx1<-rmultinom(N,n2,p1)
xx2<-rmultinom(N,n2,p2)


for( i in 1:N)
{
  if( (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))>=e1 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))>=s1  &  (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))  +  (xx2[1,i]+xx2[2,i]-(xx0[1,i]+xx0[2,i]))   >=e2 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))   +  (xx2[1,i]+xx2[3,i]-(xx0[1,i]+xx0[3,i]))  >=s2)
  {
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) < s1 )
    {
      s<-s+1
    }
  }

}
s/N
```


```{r}
dif_PCS11_sub <- function(e1,e2,s1,s2,n1,n2,pek,pe0,psk,ps0)
{
  sum<-0
  for(i in e1 : n1)
  {
    for(j in s1:n1)
    {
      
              sum<- sum + diff_prob(i,j,n1,pek,pe0,psk,ps0)
            
          
        
      
    }
  }
  sum
}

dif_PCS11_sub(e1,e2,s1,s2,n1,n2,pek,pe0,psk,ps0)


N<-100000
ss<-0
for(i in 1:N)
{
  xek<-rbinom(1,n1,pek)
  xsk<-rbinom(1,n1,psk)
  xe0<-rbinom(1,n1,pe0)
  xs0<-rbinom(1,n1,ps0)
  if(xek-xe0>=e1 & xsk-xs0>=s1)
  {
    ss<-ss+1
  }
}
ss/N

```








