---
title: "Table 2 endpoint"
author: "Chishu Yin"
date: "2023/3/22"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
a <- function(pr,pt,fi)
{
  1+(fi-1)*(pr+pt)
}

b <- function(pr,pt,fi) 
{
  -4*fi*(fi-1)*pr*pt
}

##p11,p12,p21,p22
prob <- function(pr,pt,fi)
{
  if(fi==1)
  {
    p<-c(pr*pt,pr-pr*pt,pt-pr*pt,1-pr-pt+pr*pt)
    p
  }
  else{
  a<- 1+(fi-1)*(pr+pt)
  b <- -4*fi*(fi-1)*pr*pt
  p <- matrix(nrow = 2, ncol = 2)
  p[1,1] <- round(( a - ( a^2+b )^(0.5) ) / (2*(fi-1)),digits = 4)
  p[1,2] <- round(pr-p[1,1],digits = 4)
  p[2,1] <- round(pt-p[1,1],digits = 4)
  p[2,2] <- round(1 - p[1,1] - p[1,2] - p[2,1],digits = 4)
  p <- c(p[1,1],p[1,2],p[2,1],p[2,2])
  p}
}
```



```{r}
n1<-37
n2<-49  
r1<- 1
r2<- 7
t1<- 1
t2<- 8

p_e0<-0.5
p_s0<-0.5
delta_e2<-0.2
delta_s2<-0.2
delta_e1<-0.05
delta_s1<-0.05



    p_e<- c(p_e0,p_e0+delta_e1, p_e0+delta_e1)
    p_s<- c(p_s0,p_s0+delta_s1, p_s0+delta_s1)
    
    k<- length(p_e) -1
    phi <- 2

    p00 <- matrix(data=NA,nrow = k+1,ncol=4)

    for(i in 1: (k+1))
    { 
      p00[i,] <- prob(p_e[i],p_s[i],phi)
    }
    
    
    


```



#Simulation PCS0 (pi_0 selected)
```{r}
NN<-10
result0<-seq(0,0,length=NN)

for(j in  1:NN)
{
s<-0
N<-1000

x0<-rmultinom(N,n1,p00[1,])
# x<-matrix(data = NA,nrow = k, ncol = N)
x1<-rmultinom(N,n1,p00[2,])
x2<-rmultinom(N,n1,p00[3,])

xx0<-rmultinom(N,n2,p00[1,])
#x<-matrix(data = NA,nrow = k, ncol = N)
xx1<-rmultinom(N,n2,p00[2,])
xx2<-rmultinom(N,n2,p00[3,])


for( i in 1:N)
{
  if(    (  (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))<r1 | (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))<t1  )     &    (  (x1[1,i]+x1[2,i]-(x0[1,i]+x0[2,i]))<r1 | (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i]))<t1  )  )
  {
    s<-s+1
  }
  if( (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))>=t1  &  ( (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))  +  (xx2[1,i]+xx2[2,i]-(xx0[1,i]+xx0[2,i]))   <r2 | (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))   +  (xx2[1,i]+xx2[3,i]-(xx0[1,i]+xx0[3,i]))  <t2)      )
  {
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) < t1 )
    {
      s<-s+1
    }
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]> x1[1,i]+x1[2,i])
    {
      s<-s+1
    }
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]== x1[1,i]+x1[2,i])
    {
      s<-s+1/2
    }
  }
  if( (x1[1,i]+x1[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i]))>=t1  &  ( (x1[1,i]+x1[2,i]-(x0[1,i]+x0[2,i]))  +  (xx1[1,i]+xx1[2,i]-(xx0[1,i]+xx0[2,i]))   <r2 | (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i]))   +  (xx1[1,i]+xx1[3,i]-(xx0[1,i]+xx0[3,i]))  <t2)      )
  {
    if( (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i])) < t1 )
    {
      s<-s+1
    }
    if( (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]< x1[1,i]+x1[2,i])
    {
      s<-s+1
    }
    if( (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]== x1[1,i]+x1[2,i])
    {
      s<-s+1/2
    }
  }


}
result0[j]<-s/N
}

summary(result0)
```












```{r}
p_e<- c(p_e0,p_e0+delta_e1, p_e0+delta_e2)
p_s<- c(p_s0,p_s0+delta_s1, p_s0+delta_s2)

    
    k<- length(p_e) -1  
    phi <- 2

    p <- matrix(data=NA,nrow = k+1,ncol=4)

    for(i in 1: (k+1))
    { 
      p[i,] <- prob(p_e[i],p_s[i],phi)
    }
    
    
    

p0<-p[1,] #control
p1<-p[2,]
p2<-p[3,]
```








#Simulation PCS1(pi_k selected)
```{r}
NN<-10
result<-seq(0,0,length=NN)

for(j in  1:NN)
{
s<-0
N<-10000

x0<-rmultinom(N,n1,p[1,])
# x<-matrix(data = NA,nrow = k, ncol = N)
x1<-rmultinom(N,n1,p[2,])
x2<-rmultinom(N,n1,p[3,])

xx0<-rmultinom(N,n2,p[1,])
#x<-matrix(data = NA,nrow = k, ncol = N)
xx1<-rmultinom(N,n2,p[2,])
xx2<-rmultinom(N,n2,p[3,])


for( i in 1:N)
{
  if( (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))>=t1  &  (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))  +  (xx2[1,i]+xx2[2,i]-(xx0[1,i]+xx0[2,i]))   >=r2 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))   +  (xx2[1,i]+xx2[3,i]-(xx0[1,i]+xx0[3,i]))  >=t2)
  {
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) < t1 )
    {
      s<-s+1
    }
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]> x1[1,i]+x1[2,i])
    {
      s<-s+1
    }
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]== x1[1,i]+x1[2,i])
    {
      s<-s+1/2
    }
  }

}
result[j]<-s/N
}

summary(result)
```



#Find parameters
```{r}
P1<-0.85
P0<-0.75
for(n1 in 30:50)
{
  for(n2 in 30 :50)
  {
    for(r1 in 0:10)
    {
      for(r2 in r1:15)
      {
        for(t1 in 0:10)
        {
          for(t2 in t1:15)
          {

            

            
NN<-10
result<-seq(0,0,length=NN)

for(j in  1:NN)
{
s<-0
N<-100  

x0<-rmultinom(N,n1,p00[1,])
# x<-matrix(data = NA,nrow = k, ncol = N)
x1<-rmultinom(N,n1,p00[2,])
x2<-rmultinom(N,n1,p00[3,])

xx0<-rmultinom(N,n2,p00[1,])
#x<-matrix(data = NA,nrow = k, ncol = N)
xx1<-rmultinom(N,n2,p00[2,])
xx2<-rmultinom(N,n2,p00[3,])


for( i in 1:N)
{
  if( (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))>=t1  &  (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))  +  (xx2[1,i]+xx2[2,i]-(xx0[1,i]+xx0[2,i]))   >=r2 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))   +  (xx2[1,i]+xx2[3,i]-(xx0[1,i]+xx0[3,i]))  >=t2)
  {
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) < t1 )
    {
      s<-s+1
    }
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]> x1[1,i]+x1[2,i])
    {
      s<-s+1
    }
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]== x1[1,i]+x1[2,i])
    {
      s<-s+1/2
    }
  }

}
result[j]<-s/N
}




if(mean(result)<P1)
{
  break
}




#PCS0
NN<-10
result0<-seq(0,0,length=NN)

for(j in  1:NN)
{
s<-0
N<-100

x0<-rmultinom(N,n1,p00[1,])
# x<-matrix(data = NA,nrow = k, ncol = N)
x1<-rmultinom(N,n1,p00[2,])
x2<-rmultinom(N,n1,p00[3,])

xx0<-rmultinom(N,n2,p00[1,])
#x<-matrix(data = NA,nrow = k, ncol = N)
xx1<-rmultinom(N,n2,p00[2,])
xx2<-rmultinom(N,n2,p00[3,])


for( i in 1:N)
{
  if(    (  (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))<r1 | (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))<t1  )     &    (  (x1[1,i]+x1[2,i]-(x0[1,i]+x0[2,i]))<r1 | (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i]))<t1  )  )
  {
    s<-s+1
  }
 if( (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))>=t1  &  ( (x2[1,i]+x2[2,i]-(x0[1,i]+x0[2,i]))  +  (xx2[1,i]+xx2[2,i]-(xx0[1,i]+xx0[2,i]))   <r2 | (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i]))   +  (xx2[1,i]+xx2[3,i]-(xx0[1,i]+xx0[3,i]))  <t2)        )
  {
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) < t1 )
    {
      s<-s+1
    }
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]> x1[1,i]+x1[2,i])
    {
      s<-s+1
    }
    if( (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]== x1[1,i]+x1[2,i])
    {
      s<-s+1/2
    }
  }
   if( (x1[1,i]+x1[2,i]-(x0[1,i]+x0[2,i]))>=r1 & (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i]))>=t1  &  ( (x1[1,i]+x1[2,i]-(x0[1,i]+x0[2,i]))  +  (xx1[1,i]+xx1[2,i]-(xx0[1,i]+xx0[2,i]))   <r2 | (x1[1,i]+x1[3,i]-(x0[1,i]+x0[3,i]))   +  (xx1[1,i]+xx1[3,i]-(xx0[1,i]+xx0[3,i]))  <t2)      )
  {
    if( (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i])) < t1 )
    {
      s<-s+1
    }
    if( (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]< x1[1,i]+x1[2,i])
    {
      s<-s+1
    }
    if( (x2[1,i]+x2[3,i]-(x0[1,i]+x0[3,i])) >= t1  &  x2[1,i]+x2[2,i]== x1[1,i]+x1[2,i])
    {
      s<-s+1/2
    }
  }


}
result0[j]<-s/N
}

if(mean(result0)>=P0)
{
  print(c(n1,n2,r1,r2,t1,t2))
  break
}


          }
          
        }
        
      }
      
    }
    
  }
  
  
}
```
#jiaquan(expected) sample size
#stage 1 sample size min
#normal large sample













$P(Xr=xr,Xt=xt)$
```{r}
#P(Xr=xr,Xt=xt)
joint_prob <- function(xr,xt,n1,p)
{
  sum <- 0
  for(i in max(0,xr+xt-n1) : min(xr,xt))
  {
    if(i<0 | xr-i<0 | xt-i<0 | n1-xr-xt+i<0)
    {
      sum<-sum+0
    }
    else{
    x <- c( i , xr-i , xt-i , n1-xr-xt+i )
    sum <- sum + dmultinom(x, size = NULL, prob = p, log = FALSE)
    ##cat("s = ", sum,"x =", x, "\n")
    }
  }
  sum
}
```


#function for k=2, PCS1-1 delta1=delta2, note shizi page 2-3
```{r}
#p0 control; p1, p2 are treatments, p2 selected
fct_PCS11 <- function(e1,e2,s1,s2,n1,n2,p0,p1,p2)
{
  s<-0
  for( i in 0: min(n1-e1,n1) )
  {
    for( j in max(1-s1,0): min(n1,n1-s1))
    {
      for( k in 0 : n1)
      {
        for( l in 0 : max(min(n1,s1+j-1),0) )
        {
          for( a in max(min(e1+i,n1),0) : n1)
          {
            for( b in max(min(s1+j,n1),0) : n1)
            {
              for( c in 0 : min(n2+a-i-e2,n2) )
              {
                for( d in 0 : min(n2+b-j-s2,n2))
                {
                  for(e in max(min(e2+i+c-a,n2),0) : n2)
                  {
                    for(f in max(min(s2+j+d-b,n2),0) : n2)
                    {
                      
                     #if(   s1+j-1<0 | e1+i>n1  | s1+j>n1 | e2+i+c-a>n1  | s2+j+d-b>n1 )
                      #if( n2+a-i-e2<0 | n2+b-j-s2<0 | i<0 | j<0 | k<0 | l<0 | a<0 | b<0| c<0| d<0 | e<0 | f<0)
                      #{
                      #  s<-s+0
                      #}
                      
                      #else
                      {
                        s <- s + joint_prob(i,j,n1,p0) * joint_prob(k,l,n1,p1) * joint_prob(a,b,n1,p2) * joint_prob(c,d,n2,p0) * joint_prob(e,f,n2,p2)
                      }
                      
                      
                      
                      
                    }
                  }
                }
              }
            }
          }
        }
      }
    }
  }
  s
}
```

#function for k=2, PCS1-2 delta1=delta2, note shizi page 2-3
```{r}
#p0 control; p1, p2 are treatments, p2 selected
fct_PCS12 <- function(e1,e2,s1,s2,n1,n2,p0,p1,p2)
{
  s<-0
  for(i in 0: min(n1,n1-e1))
  {
    for(j in 0 : min(n1,n1-s1))
    {
      for(k in 0 : (n1-1))
      {
        for(l in max(s1+j,0) : n1)
        {
          for(a in max(max(e1+i,k+1),i+e2-n2) : n1)
          {
            for(b in max(max(s1+j,0),s2+j-n2) : n1)
            {
              for(c in 0: min(n2, n2+a-i-e2))
              {
                for(d in 0 : min(n2, n2+b-s2-j))
                {
                  for(e in max(e2+i+c-a,0) : n2)
                  {
                    for(f in max(s2+j+d-b,0) : n2)
                    {
                       s <- s + joint_prob(i,j,n1,p0) * joint_prob(k,l,n1,p1) * joint_prob(a,b,n1,p2) * joint_prob(c,d,n2,p0) * joint_prob(e,f,n2,p2)
                    }
                  }
                }
              }
            }
          }
        }
      }
    }
  }
  s
}
```  



#function for k=2, PCS1-3 delta1=delta2, note shizi page 2-3
```{r}
#p0 control; p1, p2 are treatments, p2 selected
fct_PCS13 <- function(e1,e2,s1,s2,n1,n2,p0,p1,p2)
{
  s<-0
  for(i in 0: min(n1,n1-e1))
  {
    for(j in 0 : min(n1,n1-s1))
    {
      for(k in max(e1+i,0) : n1)
      {
        for(l in max(s1+j,0) : n1)
        {
          
          {
            for(b in max(max(s1+j,0),s2+j-n2) : n1)
            {
              for(c in 0: min(n2, n2+k-i-e2))
              {
                for(d in 0 : min(n2, n2+b-s2-j))
                {
                  for(e in max(e2+i+c-k,0) : n2)
                  {
                    for(f in max(s2+j+d-b,0) : n2)
                    {
                       s <- s + joint_prob(i,j,n1,p0) * joint_prob(k,l,n1,p1) * joint_prob(k,b,n1,p2) * joint_prob(c,d,n2,p0) * joint_prob(e,f,n2,p2)
                    }
                  }
                }
              }
            }
          }
        }
      }
    }
  }
  s/2
}
```  




#PCS1=PCS11+PCS12+PCS13
```{r}
#p0 control; p1, p2 are treatments, p2 selected
fct_PCS1 <- function(e1,e2,s1,s2,n1,n2,p0,p1,p2)
{
  fct_PCS11(e1,e2,s1,s2,n1,n2,p0,p1,p2)+fct_PCS12(e1,e2,s1,s2,n1,n2,p0,p1,p2)+fct_PCS13(e1,e2,s1,s2,n1,n2,p0,p1,p2)
}
```


#test
```{r}
fct_PCS1(r1,r2,t1,t2,n1,n2,p0,p1,p2)
```

simulation check exact run time
normal approximation